\vspace{-.2in} Squint: Lossy Hierarchical Compression on Symbol Streams \vspace{-.1in}

### 2012-12-12 tex/paper.tex
minor changes to larger tests

In both datasets, the compression ratios achieved for both algorithms are
roughly equal given the same value for $\epsilon$, so it is fair to compare the
algorithms for the same values of $\epsilon$.  From plotting the data, we see
that runtime of the algorithms are roughly polynomial in the size of the data,
so we can perform a linear regression on the log-log transform of the data to
find the exponents $\alpha$ for the runtime $r(n)=n^\alpha$ where $n$ is the
length of the input string. In the charts below, all of the linear regressions
had $R^2$ values of over $0.98$.
\begin{align*}
  \text{rep-n:}\quad
  \begin{array}{l|l|l||l|l}
    & \multicolumn{2}{c||}{\Similarity} & \multicolumn{2}{c}{\Cluster} \\ \hline
    \epsilon & .4 & .2 & .4 & .2 \\
    \alpha   & 1.859 & 2.026 & 1.306 & 1.305
  \end{array}
  &&
  \text{gen-n:}\quad
  \begin{array}{l|l|l||l|l}
    & \multicolumn{2}{c||}{\Similarity} & \multicolumn{2}{c}{\Cluster} \\ \hline
    \epsilon & .4 & .2 & .4 & .2 \\
    \alpha   & 2.629 & 2.493 & 1.814 & 2.061
  \end{array}
\end{align*}

@@

>>>>

In both datasets, the compression ratios achieved for both algorithms are
roughly equal given the same value for $\epsilon$, so it is fair to compare the
algorithms for the same values of $\epsilon$.  From plotting the data, we see
that runtime of the algorithms are roughly polynomial in the size of the data,
so we can perform a linear regression on the log-log transform of the data to
find the exponents $\alpha$ for the runtime $r(n)=n^\alpha$ where $n$ is the
length of the input string. In the charts below, all of the linear regressions
had $R^2$ values of over $0.98$.

\begin{tabular}{l|l|l|l|l}
rep-n runtime & Sim: $\epsilon=.4$ & Sim: $\epsilon=.2$ & Clust: $\epsilon = .4$ & Clust: $\epsilon = .2$ \\
Exponent      & $1.859$ & $2.026$ & $1.306$ & $1.305$
\end{tabular}

\begin{tabular}{l|l|l|l|l}
gen-n runtime & Sim: $\epsilon=.4$ & Sim: $\epsilon=.2$ & Clust: $\epsilon = .4$ & Clust: $\epsilon = .2$ \\
Exponent      & $2.629$ & $2.493$ & $1.814$ & $2.061$
\end{tabular}

@@

\subsection*{Output:}
